Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-11 article/article.tex
PCA results

From Table~\ref{tab:results} we can distinguish the fact that when PCA is used for feature extraction, the performance of GNB is lower than when other feature selection methods are used. The confidence interval of the predictive performance of GNB when PCA is used is 95\% $CI: 56.9 - 65.8$ which is significantly worse than other dimension reduction techniques. This suggests that maximizing the variance of the data does not maximize information. Another explanation could be that the data is not suited to be aligned by voxel index (see section~\ref{sec:dimensionalityReduction}). The performance listed in Table~\ref{tab:results} is for PCA using 149 components. This value was found by performing classification with a varying amount of components, the results for which are listed in figure~\ref{fig:pca_components}.

>>>>

From Table~\ref{tab:results} we can distinguish the fact that when PCA is used for feature extraction, the performance of GNB is lower than when other feature selection methods are used. The confidence interval of the predictive performance of GNB when PCA is used is 95\% $CI: 56.9 - 65.8$ which is significantly worse than applying GNB in combination with other feature selection methods. This suggests that maximizing the variance of the data does not maximize information. Another explanation could be that the data is not suited to be aligned by voxel index (see section~\ref{sec:dimensionalityReduction}). The performance listed in Table~\ref{tab:results} is for PCA using 149 components. This value was found by performing classification with a varying amount of components, the results for which are listed in figure~\ref{fig:pca_components}.
